CLT Results

### 2022-04-01 analysis/clt_irt_analysis.Rmd
prep run dif model cluster

```{r}
irt_dat <- data%>%
  select(subjID, targetWord, correct)
```

@@

```{r}
irt3 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (1 |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (1 |i| targetWord),
    nl = TRUE
  ),
  prior = prior_va_3pl,
  cores = 6,
  chains = 6,
  iter = 6000
)

saveRDS(irt3, "../saves/irt3.rds")
```

>>>>

```{r}
irt_dat <- data%>%
  select(subjID, targetWord, correct, order, sex)
```

@@

```{r}
irt3_dif <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (sex |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (sex |i| targetWord),
    nl = TRUE
  ),
  prior = prior_va_3pl,
  cores = 6,
  chains = 6,
  iter = 6000
)

saveRDS(irt3_dif, "../saves/irt3_dif.rds")
```
